Towards Contract Modules for the Tezos Blockchain

### 2021-05-14 papers/contract-modules/fmbc2021/fmbc-main.tex
Update fmbc-main.tex

\author{Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

@@

\authorrunning{Ha Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

>>>>

\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

@@

\authorrunning{T.T.H Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
